--- 
title: "Medical Distribution Business Analysis Report (Excluding Pharmaceuticals)"
subtitle: "Hospital Consumption Data Analysis - 13 Month Study (Non-Pharma Focus)"
author: "Medical Distribution Business Analysis"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    number_sections: true
    code_folding: hide
    df_print: paged
    fig_width: 12
    fig_height: 8
---

```{css, echo=FALSE}
/* Custom CSS for professional look */
body {
  font-family: 'Segoe UI', Tahoma, Geneva, Verdana, sans-serif;
  line-height: 1.6;
}

.main-container {
  max-width: 1200px;
}

h1, h2, h3 {
  color: #2c3e50;
}

.alert {
  padding: 15px;
  margin-bottom: 20px;
  border: 1px solid transparent;
  border-radius: 4px;
}

.alert-success {
  background-color: #d4edda;
  border-color: #c3e6cb;
  color: #155724;
}

.alert-info {
  background-color: #d1ecf1;
  border-color: #bee5eb;
  color: #0c5460;
}

.alert-warning {
  background-color: #fff3cd;
  border-color: #ffeaa7;
  color: #856404;
}

.kpi-box {
  background: linear-gradient(135deg, #667eea 0%, #764ba2 100%);
  color: white;
  padding: 20px;
  border-radius: 10px;
  text-align: center;
  margin: 10px;
}

.kpi-number {
  font-size: 2em;
  font-weight: bold;
}

.kpi-label {
  font-size: 0.9em;
  opacity: 0.9;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = 'center',
  cache = TRUE
)

# Function to install and load packages
install_and_load <- function(packages) {
  for (package in packages) {
    if (!require(package, character.only = TRUE)) {
      install.packages(package, dependencies = TRUE)
      library(package, character.only = TRUE)
    }
  }
}

# Required packages
required_packages <- c(
  "readr", "dplyr", "ggplot2", "plotly", "DT", 
  "lubridate", "tidyr", "scales", "knitr", 
  "kableExtra", "gridExtra", "viridis", "zoo"
)

# Install and load packages
install_and_load(required_packages)

# Try to load optional packages
if (!require(treemapify, quietly = TRUE)) {
  message("treemapify package not available - treemap visualization will be skipped")
  treemap_available <- FALSE
} else {
  treemap_available <- TRUE
}
```

```{r load-data, include=FALSE}
# Load and prepare data
# Update this path to your CSV file location
data <- read_csv("cleanedup_data_and_merged_and_refined.csv")

# Data cleaning
colnames(data) <- gsub(" ", "_", colnames(data))
data <- data %>%
  mutate(
    Date = paste(YEAR, MONTH, "01", sep = "-"),
    Date = as.Date(Date, format = "%Y-%B-%d"),
    Month_Year = format(Date, "%Y-%m"),
    ITEM_NAME = trimws(ITEM_NAME),
    VENDOR = trimws(VENDOR),
    CATEGORY = trimws(CATEGORY)
  )

# CATEGORY FILTERING SETUP
# Define categories for filtering (you can modify this list)
available_categories <- sort(unique(data$CATEGORY))
print(paste("Available categories:", paste(available_categories, collapse = ", ")))

# FILTERING FUNCTION
filter_data_by_categories <- function(data, selected_categories = NULL) {
  if (is.null(selected_categories) || length(selected_categories) == 0) {
    return(data)  # Return all data if no filter specified
  }
  return(data %>% filter(CATEGORY %in% selected_categories))
}

# SET YOUR CATEGORY FILTER HERE
# This script will EXCLUDE 'Pharmaceuticals'
selected_categories <- available_categories[!available_categories %in% c("Pharmaceuticals")]

# Apply filter
if (!is.null(selected_categories)) {
  filtered_data <- filter_data_by_categories(data, selected_categories)
  filter_message <- paste("Filtered to categories (excluding Pharmaceuticals):", paste(selected_categories, collapse = ", "))
} else {
  # This else block should ideally not be reached if Pharmaceuticals is always excluded
  filtered_data <- data %>% filter(!CATEGORY %in% c("Pharmaceuticals")) # Failsafe
  filter_message <- "All categories EXCLUDING Pharmaceuticals (failsafe)"
}

# Calculate key metrics (on filtered data)
total_records <- nrow(filtered_data)
total_quantity <- sum(filtered_data$QUANTITY, na.rm = TRUE)
unique_items <- n_distinct(filtered_data$ITEM_NAME)
unique_vendors <- n_distinct(filtered_data$VENDOR)
unique_categories <- n_distinct(filtered_data$CATEGORY)
date_range <- paste(min(filtered_data$Date, na.rm = TRUE), "to", max(filtered_data$Date, na.rm = TRUE))
```

# Executive Summary {.tabset}

<div class="alert alert-success">
<strong>Key Finding:</strong> This analysis (excluding Pharmaceuticals) reveals significant opportunities for a medical distribution business to optimize hospital supply chains, with potential market entry points worth over `r format(total_quantity, big.mark = ",")` units annually across `r unique_categories` medical categories.
</div>

<div class="alert alert-info">
<strong>Current Filter:</strong> `r filter_message`<br>
<strong>Available Categories (in original dataset):</strong> `r paste(available_categories, collapse = ", ")`<br>
</div>

## Key Performance Indicators

<div style="display: flex; flex-wrap: wrap;">
<div class="kpi-box" style="flex: 1;">
<div class="kpi-number">`r format(total_quantity, big.mark = ",")`</div>
<div class="kpi-label">Total Units Consumed (Non-Pharma)</div>
</div>

<div class="kpi-box" style="flex: 1;">
<div class="kpi-number">`r unique_items`</div>
<div class="kpi-label">Unique Products (Non-Pharma)</div>
</div>

<div class="kpi-box" style="flex: 1;">
<div class="kpi-number">`r unique_vendors`</div>
<div class="kpi-label">Current Vendors (Non-Pharma)</div>
</div>

<div class="kpi-box" style="flex: 1;">
<div class="kpi-number">13</div>
<div class="kpi-label">Months of Data</div>
</div>
</div>

## Strategic Recommendations

<div class="alert alert-info">
<strong>Immediate Opportunities (Non-Pharma Focus):</strong>
<ul>
<li><strong>Focus on A-Class Items:</strong> Identify the 20% of non-pharmaceutical products driving 80% of volume.</li>
<li><strong>Vendor Consolidation:</strong> Explore consolidating suppliers for non-pharmaceutical items.</li>
</ul>
<strong>Longer-Term Strategy (Non-Pharma Focus):</strong>
<ul>
<li><strong>Market Expansion:</strong> Grow market share in high-potential non-pharmaceutical categories.</li>
<li><strong>Inventory Optimization:</strong> Fine-tune stock levels for key non-pharmaceutical products.</li>
</ul>
</div>

# Market Analysis (Excluding Pharmaceuticals) {.tabset}

## ABC Classification Analysis

### What is ABC Analysis?

<div class="alert alert-warning">
<p>ABC analysis is an inventory categorization technique that classifies items based on their consumption value. This helps prioritize management efforts:</p>
<ul>
<li><strong>Class A (High Priority):</strong> Items representing approximately <strong>80% of consumption volume</strong> but only <strong>20% of total items</strong>. These require tight control, accurate forecasting, and secure supplier relationships.</li>
<li><strong>Class B (Medium Priority):</strong> Items representing approximately <strong>15% of consumption volume</strong> and <strong>30% of items</strong>. These require moderate control with periodic reviews and standard ordering procedures.</li>
<li><strong>Class C (Low Priority):</strong> Items representing only <strong>5% of consumption volume</strong> but <strong>50% of total items</strong>. These can be managed with simple controls, bulk ordering, or just-in-time delivery.</li>
</ul>
<strong>Benefits:</strong>
<ul>
<li>💰 <strong>Cost Savings:</strong> Reduced inventory holding costs</li>
<li>📈 <strong>Improved Service:</strong> Better availability of critical items</li>
<li>⚡ <strong>Efficient Operations:</strong> Different management strategies for different item classes</li>
</ul>
</div>

```{r abc-analysis}
# Perform ABC Analysis (on filtered data)
abc_analysis <- filtered_data %>%
  group_by(ITEM_NAME, CATEGORY) %>%
  summarise(
    Total_Quantity = sum(QUANTITY, na.rm = TRUE),
    Transaction_Count = n(),
    Avg_Quantity_Per_Transaction = mean(QUANTITY, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  filter(Total_Quantity > 0) %>% # Ensure only items with consumption are included
  arrange(desc(Total_Quantity)) %>%
  mutate(
    Cumulative_Quantity = cumsum(Total_Quantity),
    Percentage_of_Total = (Total_Quantity / sum(Total_Quantity)) * 100,
    Cumulative_Percentage = (Cumulative_Quantity / sum(Total_Quantity)) * 100,
    ABC_Class = case_when(
      Cumulative_Percentage <= 80 ~ "A",
      Cumulative_Percentage <= 95 ~ "B",
      TRUE ~ "C"
    )
  )

# Summary of ABC classes
abc_summary <- abc_analysis %>%
  group_by(ABC_Class) %>%
  summarise(
    Number_of_Items = n(),
    Percentage_of_Items = (n() / nrow(abc_analysis)) * 100,
    Total_Volume = sum(Total_Quantity),
    Percentage_of_Volume = (sum(Total_Quantity) / sum(abc_analysis$Total_Quantity)) * 100,
    .groups = 'drop'
  )

abc_caption <- ifelse(
  is.null(selected_categories) || length(selected_categories) == length(available_categories[!available_categories %in% c("Pharmaceuticals")]) , 
  "ABC Analysis Summary - All Non-Pharmaceutical Categories", 
  paste("ABC Analysis Summary - Filtered to (Excluding Pharmaceuticals):", paste(selected_categories, collapse = ", "))
)

kable(abc_summary, 
      caption = abc_caption,
      format.args = list(big.mark = ",")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### Top 20 High-Priority Items (Class A - Non-Pharma)

```{r top-items-table}
top_items <- abc_analysis %>%
  filter(ABC_Class == "A") %>%
  head(20) %>%
  select(ITEM_NAME, CATEGORY, Total_Quantity, Transaction_Count, Percentage_of_Total) %>%
  mutate(
    Total_Quantity = format(Total_Quantity, big.mark = ","),
    Percentage_of_Total = round(Percentage_of_Total, 2)
  )

DT::datatable(top_items, 
              caption = "Top 20 Class A Items (Excluding Pharmaceuticals)",
              options = list(pageLength = 10, dom = 'ft'),
              rownames = FALSE,
              class = 'cell-border stripe')
```

<div class="alert alert-info">
<strong>Note:</strong> These are the top 20 Class A items based on the current filter (excluding Pharmaceuticals). They represent the most significant products by volume in the selected non-pharmaceutical categories.
</div>

### ABC Analysis Visualization

```{r abc-visualization, fig.height=10}
# ABC Distribution Chart
abc_plot1 <- ggplot(abc_summary, aes(x = ABC_Class, y = Percentage_of_Volume, fill = ABC_Class)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(round(Percentage_of_Volume, 1), "%")), 
            vjust = -0.5, color = "black", size = 4) +
  labs(title = "ABC Analysis: Percentage of Volume by Class (Non-Pharma)",
       x = "ABC Class", y = "Percentage of Total Volume") +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(plot.title = element_text(size = 14, hjust = 0.5))

# Pareto Chart (Cumulative Percentage)
abc_plot2 <- ggplot(abc_analysis, aes(x = reorder(ITEM_NAME, -Total_Quantity))) +
  geom_bar(aes(y = Total_Quantity, fill = ABC_Class), stat = "identity") +
  geom_line(aes(y = Cumulative_Quantity, group = 1), color = "red", size = 1) +
  scale_y_continuous(name = "Total Quantity", 
                     labels = comma, 
                     sec.axis = sec_axis(~./sum(abc_analysis$Total_Quantity)*100, 
                                         name = "Cumulative Percentage (%)")) +
  labs(title = "Pareto Chart of Item Consumption (Non-Pharma)", 
       subtitle = "Top 50 items shown for clarity",
       x = "Item Name (Ranked by Volume)", y = "Total Quantity") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, hjust = 0.5),
    axis.text.x = element_blank(), # Hide item names for clarity, too many to display
    axis.ticks.x = element_blank()
  ) +
  coord_cartesian(xlim = c(0, 50)) # Limit to top 50 items for visualization

grid.arrange(abc_plot1, abc_plot2, nrow = 2)
```

## ABC Analysis Summary & Strategic Implications

```{r abc-summary-insights}
# Calculate detailed ABC insights
abc_insights <- abc_analysis %>%
  group_by(ABC_Class) %>%
  summarise(
    Number_of_Items = n(),
    Total_Volume = sum(Total_Quantity),
    Avg_Volume_per_Item = mean(Total_Quantity),
    .groups = 'drop'
  ) %>%
  mutate(
    Percentage_of_Items = (Number_of_Items / sum(Number_of_Items)) * 100,
    Percentage_of_Volume = (Total_Volume / sum(Total_Volume)) * 100
  )

class_a_volume_pct <- round(abc_insights$Percentage_of_Volume[abc_insights$ABC_Class == "A"], 1)
class_a_items_pct <- round(abc_insights$Percentage_of_Items[abc_insights$ABC_Class == "A"], 1)

top_single_item <- abc_analysis$ITEM_NAME[1]
top_item_volume <- format(abc_analysis$Total_Quantity[1], big.mark = ",")
top_item_pct <- round(abc_analysis$Percentage_of_Total[1], 2)
```

<div class="alert alert-success">
<h4>🎯 ABC Analysis Key Findings (Non-Pharma)</h4>
<ul>
<li><strong>Class A items:</strong> Represent <strong>`r class_a_volume_pct`%</strong> of total non-pharmaceutical consumption volume from just <strong>`r class_a_items_pct`%</strong> of unique non-pharmaceutical items.</li>
<li><strong>Top Item:</strong> The single highest volume non-pharmaceutical item, <strong>`r top_single_item`</strong>, accounts for <strong>`r top_item_volume`</strong> units (`r top_item_pct`% of total non-pharma volume).</li>
<li><strong>Focus Area:</strong> Concentrating efforts on Class A non-pharmaceutical items offers the highest return on investment for inventory management and supplier negotiation.</li>
</ul>

<strong>Operational Recommendations:</strong>
<ul>
<li><strong>Class A:</strong> Daily monitoring, safety stock, multiple suppliers, premium service</li>
<li><strong>Class B:</strong> Weekly reviews, standard inventory policies, regular supplier relationships</li>
<li><strong>Class C:</strong> Monthly/quarterly reviews, bulk ordering, consider dropshipping</li>
</ul>
</div>

# Category Performance Analysis

```{r category-performance-analysis}
# Category performance metrics (on filtered data)
category_performance <- filtered_data %>%
  group_by(CATEGORY) %>%
  summarise(
    Total_Transactions = n(),
    Total_Quantity = sum(QUANTITY, na.rm = TRUE),
    Unique_Items = n_distinct(ITEM_NAME),
    Unique_Vendors = n_distinct(VENDOR),
    Avg_Transaction_Size = mean(QUANTITY, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  arrange(desc(Total_Quantity)) %>%
  mutate(
    Percentage_of_Total = (Total_Quantity / sum(Total_Quantity)) * 100,
    Market_Priority = case_when(
      Percentage_of_Total >= 20 ~ "High Priority",
      Percentage_of_Total >= 5 ~ "Medium Priority",
      TRUE ~ "Low Priority"
    )
  )

# Display category performance table
category_table_caption <- ifelse(
  is.null(selected_categories) || length(selected_categories) == length(available_categories[!available_categories %in% c("Pharmaceuticals")]) , 
  "Category Performance Analysis - All Non-Pharmaceutical Categories", 
  paste("Category Performance Analysis - Filtered to (Excluding Pharmaceuticals):", paste(selected_categories, collapse = ", "))
)

# Create and display the table using DT instead of kable for better HTML rendering
category_table <- category_performance %>%
  mutate(
    Total_Quantity = format(Total_Quantity, big.mark = ","),
    Avg_Transaction_Size = round(Avg_Transaction_Size, 1),
    Percentage_of_Total = paste0(round(Percentage_of_Total, 1), "%")
  )

# Print the caption
cat(paste0("<h4>", category_table_caption, "</h4>"))

# Use DT::datatable for better HTML rendering
DT::datatable(category_table, 
              options = list(pageLength = 10, dom = 'ft'),
              rownames = FALSE,
              class = 'cell-border stripe')
```

<div class="alert alert-info">
<strong>🔍 Category Filtering Options:</strong><br>
This report is pre-filtered to exclude 'Pharmaceuticals'. To analyze other specific non-pharmaceutical categories, you can modify the `selected_categories` variable at the top of the report further, for example:<br>
<code>selected_categories <- available_categories[!available_categories %in% c("Pharmaceuticals", "AnotherCategoryToExclude")]</code><br>
<em>Current filter: `r ifelse(is.null(selected_categories) || length(selected_categories) == length(available_categories[!available_categories %in% c("Pharmaceuticals")]) , "All Non-Pharmaceutical Categories Shown", paste(selected_categories, collapse = ", "))`</em>
</div>

## Category Distribution Visualization

```{r category-visualization, fig.height=12}
# Category pie chart
pie_plot <- ggplot(category_performance, aes(x = "", y = Percentage_of_Total, fill = CATEGORY)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  labs(title = "Market Share by Category (Excluding Pharmaceuticals)") +
  theme_void() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    legend.position = "right"
  ) +
  geom_text(aes(label = paste0(CATEGORY, "\n", round(Percentage_of_Total, 1), "%")), 
            position = position_stack(vjust = 0.5), 
            color = "white", size = 3.5) +
  scale_fill_viridis_d()

# Category bar chart (volume)
bar_plot <- ggplot(category_performance, aes(x = reorder(CATEGORY, -Total_Quantity), y = Total_Quantity, fill = CATEGORY)) +
  geom_bar(stat = "identity") +
  labs(title = "Total Volume by Category (Excluding Pharmaceuticals)", 
       x = "Category", y = "Total Quantity Consumed") +
  scale_y_continuous(labels = comma) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none"
  ) +
  scale_fill_viridis_d()

# Treemap if package available
if(treemap_available) {
  treemap_plot <- ggplot(category_performance, 
                         aes(area = Total_Quantity, fill = CATEGORY, label = paste(CATEGORY, scales::comma(Total_Quantity), sep = "\n"))) +
    geom_treemap() +
    geom_treemap_text(fontface = "italic", colour = "white", place = "centre", grow = TRUE) +
    labs(title = "Treemap of Category Volume (Excluding Pharmaceuticals)") +
    theme(legend.position = "none", plot.title = element_text(size = 16, hjust = 0.5)) +
    scale_fill_viridis_d()
  
  grid.arrange(pie_plot, bar_plot, treemap_plot, ncol = 1, heights = c(1,1,1.2))
} else {
  grid.arrange(pie_plot, bar_plot, ncol = 1, heights = c(1,1))
}
```

# Vendor Analysis (Excluding Pharmaceuticals)

```{r vendor-analysis}
# Vendor performance metrics (on filtered data)
vendor_performance <- filtered_data %>%
  group_by(VENDOR) %>%
  summarise(
    Total_Transactions = n(),
    Total_Quantity = sum(QUANTITY, na.rm = TRUE),
    Unique_Items_Supplied = n_distinct(ITEM_NAME),
    Avg_Transaction_Size = mean(QUANTITY, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  filter(Total_Quantity > 0) %>% # Ensure only vendors with sales are included
  arrange(desc(Total_Quantity)) %>%
  mutate(
    Percentage_of_Total_Volume = (Total_Quantity / sum(Total_Quantity)) * 100,
    Vendor_Tier = case_when(
      Percentage_of_Total_Volume >= 10 ~ "Tier 1 (Key Supplier)",
      Percentage_of_Total_Volume >= 1 ~ "Tier 2 (Regular Supplier)",
      TRUE ~ "Tier 3 (Occasional Supplier)"
    )
  )

# Display vendor performance table (Top 20)
vendor_table_caption <- ifelse(
  is.null(selected_categories) || length(selected_categories) == length(available_categories[!available_categories %in% c("Pharmaceuticals")]) , 
  "Top 20 Vendor Performance (All Non-Pharmaceutical Categories)", 
  paste("Top 20 Vendor Performance (Filtered Non-Pharma Categories):", paste(selected_categories, collapse = ", "))
)

# Create and display the table
vendor_table_display <- vendor_performance %>%
  head(20) %>%
  mutate(
    Total_Quantity = format(Total_Quantity, big.mark = ","),
    Avg_Transaction_Size = round(Avg_Transaction_Size, 1),
    Percentage_of_Total_Volume = paste0(round(Percentage_of_Total_Volume, 1), "%")
  )

cat(paste0("<h4>", vendor_table_caption, "</h4>"))
DT::datatable(vendor_table_display, 
              options = list(pageLength = 10, dom = 'ft'),
              rownames = FALSE,
              class = 'cell-border stripe')
```

<div class="alert alert-info">
<strong>Vendor Consolidation Opportunity:</strong> Analyze Tier 3 vendors (supplying <1% of total volume) for potential consolidation to streamline procurement and potentially negotiate better terms with Tier 1 or Tier 2 suppliers.
</div>

## Vendor Distribution Visualization

```{r vendor-visualization, fig.height=10}
# Top N vendors for visualization
top_n_vendors <- 15
vendor_plot_data <- vendor_performance %>%
  head(top_n_vendors)

# Vendor bar chart (volume)
vendor_bar_plot <- ggplot(vendor_plot_data, aes(x = reorder(VENDOR, -Total_Quantity), y = Total_Quantity, fill = VENDOR)) +
  geom_bar(stat = "identity") +
  labs(title = paste("Top", top_n_vendors, "Vendors by Volume (Excluding Pharmaceuticals)"), 
       x = "Vendor", y = "Total Quantity Supplied") +
  scale_y_continuous(labels = comma) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none"
  ) +
  scale_fill_viridis_d(option = "plasma")

# Vendor pie chart (market share)
vendor_pie_plot <- ggplot(vendor_plot_data, aes(x = "", y = Percentage_of_Total_Volume, fill = VENDOR)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  labs(title = paste("Market Share of Top", top_n_vendors, "Vendors (Excluding Pharmaceuticals)")) +
  theme_void() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    legend.position = "right"
  ) +
  geom_text(aes(label = paste0(round(Percentage_of_Total_Volume,1),"%")), 
            position = position_stack(vjust = 0.5), 
            color = "white", size=3) +
  scale_fill_viridis_d(option = "plasma")

grid.arrange(vendor_bar_plot, vendor_pie_plot, ncol = 1, heights = c(1.2, 1))
```

# Time Series Analysis (Excluding Pharmaceuticals)

```{r time-series-analysis}
# Monthly trends (on filtered data)
monthly_trends <- filtered_data %>%
  group_by(Month_Year) %>%
  summarise(
    Total_Quantity = sum(QUANTITY, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  mutate(
    Date = as.Date(paste0(Month_Year, "-01"), format = "%Y-%m-%d"),
    Moving_Avg_3M = zoo::rollmean(Total_Quantity, k = 3, fill = NA, align = "right"),
    Growth_Rate = ((Total_Quantity / lag(Total_Quantity)) - 1) * 100
  ) %>%
  arrange(Date)

# Display monthly trends table
monthly_trends_table_caption <- ifelse(
  is.null(selected_categories) || length(selected_categories) == length(available_categories[!available_categories %in% c("Pharmaceuticals")]) , 
  "Monthly Consumption Trends (All Non-Pharmaceutical Categories)", 
  paste("Monthly Consumption Trends (Filtered Non-Pharma Categories):", paste(selected_categories, collapse = ", "))
)

monthly_trends_display <- monthly_trends %>%
  mutate(
    Total_Quantity = format(Total_Quantity, big.mark = ","),
    Moving_Avg_3M = ifelse(is.na(Moving_Avg_3M), "N/A", format(round(Moving_Avg_3M,0), big.mark = ",")),
    Growth_Rate = ifelse(is.na(Growth_Rate), "N/A", paste0(round(Growth_Rate, 1), "%"))
  ) %>% select(-Date)

cat(paste0("<h4>", monthly_trends_table_caption, "</h4>"))
DT::datatable(monthly_trends_display, 
              options = list(pageLength = nrow(monthly_trends_display), dom = 't'), # Show all months, no search/paging
              rownames = FALSE,
              class = 'cell-border stripe')
```

## Monthly Trend Visualization

```{r monthly-trend-visualization, fig.height=10}
# Monthly consumption plot
monthly_plot <- ggplot(monthly_trends, aes(x = Date)) +
  geom_line(aes(y = Total_Quantity, group = 1), color = "dodgerblue", size = 1) +
  geom_point(aes(y = Total_Quantity, group = 1), color = "dodgerblue", size = 2) +
  geom_line(aes(y = Moving_Avg_3M, group = 1), color = "orange", size = 1, linetype = "dashed") +
  labs(title = "Monthly Consumption Trends (Excluding Pharmaceuticals)",
       subtitle = "Blue line: Actual consumption, Orange line: 3-month moving average",
       x = "Month-Year", y = "Total Quantity") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 12, hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "1 month", date_labels = "%Y-%m")

# Growth rate plot
growth_plot <- ggplot(monthly_trends %>% filter(!is.na(Growth_Rate)), 
                     aes(x = Date, y = Growth_Rate)) +
  geom_bar(stat = "identity", fill = "lightcoral") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(title = "Month-over-Month Growth Rate (Excluding Pharmaceuticals)",
       x = "Month-Year", y = "Growth Rate (%)") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  scale_x_date(date_breaks = "1 month", date_labels = "%Y-%m")

grid.arrange(monthly_plot, growth_plot, nrow = 2)
```

# Business Recommendations

## Priority Action Items (Non-Pharma Focus)

<div class="alert alert-success">
<h4>Immediate Actions (Week 1-2)</h4>
<ol>
<li><strong>Focus on Top 20 A-Class Non-Pharma Items:</strong> These represent your highest-volume, lowest-risk market entry points within non-pharmaceuticals.</li>
<li><strong>Research Pricing for Key Non-Pharma Items:</strong> Obtain wholesale prices for top non-pharma consumables identified.</li>
<li><strong>Vendor Outreach (Non-Pharma):</strong> Contact smaller suppliers of non-pharmaceuticals for potential partnerships or consolidation.</li>
</ol>
</div>

<div class="alert alert-info">
<h4>Medium-term Strategy (Month 1-3)</h4>
<ol>
<li><strong>Category Specialization (Non-Pharma):</strong> Deepen focus on high-volume/high-margin non-pharmaceutical categories.</li>
<li><strong>Inventory Optimization (Non-Pharma):</strong> Develop reorder points for high-volume non-pharma consumables.</li>
<li><strong>Customer Acquisition:</strong> Use this hospital's non-pharma consumption patterns to target similar healthcare facilities.</li>
</ol>
</div>

<div class="alert alert-warning">
<h4>Long-term Goals (3-12 months)</h4>
<ol>
<li><strong>Technology Integration:</strong> Implement automated ordering systems for non-pharma supplies.</li>
<li><strong>Geographic Expansion:</strong> Scale successful non-pharma model to other regions.</li>
<li><strong>Value-added Services:</strong> Offer inventory management and forecasting services for non-pharmaceuticals.</li>
</ol>
</div>

## Financial Projections (Based on Non-Pharma Volume)

```{r financial-projections}
# Simple financial model based on non-pharma volume
financial_model <- data.frame(
  Scenario = c("Conservative", "Moderate", "Aggressive"),
  Market_Penetration_Non_Pharma = c("10%", "25%", "40%"),
  Annual_Volume_Non_Pharma = c(
    format(total_quantity * 0.1, big.mark = ","),
    format(total_quantity * 0.25, big.mark = ","),
    format(total_quantity * 0.4, big.mark = ",")
  ),
  Estimated_Revenue_Range_Non_Pharma = c("$200K - $400K", "$500K - $1M", "$800K - $1.5M") # Example figures
)

kable(financial_model,
      caption = "Revenue Projections Based on Non-Pharmaceutical Market Penetration") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

---

<div style="text-align: center; margin-top: 40px; padding: 20px; background-color: #f8f9fa; border-radius: 10px;">
<h3>Report Generated on `r Sys.Date()`</h3>
<p>This analysis is based on 13 months of actual hospital consumption data (Excluding Pharmaceuticals)<br>
Total records analyzed: `r format(total_records, big.mark = ",")`<br>
Data period: `r date_range`<br>
<strong>Current filter: `r filter_message`</strong></p>

<div class="alert alert-info" style="margin-top: 20px;">
<h4>🔧 How to Further Filter Categories</h4>
<p>This report already excludes 'Pharmaceuticals'. To further refine the analysis on the remaining categories, modify this line in the data loading section:</p>
<code>selected_categories <- available_categories[!available_categories %in% c("Pharmaceuticals", "CategoryToExclude1", "CategoryToExclude2")]</code>

<p><strong>Available non-pharmaceutical categories in this report:</strong><br>
`r paste(paste0('"', selected_categories, '"'), collapse = ", ")`</p>
</div>
</div>
