---
title: "Medical Distribution Business Analysis - Non-Pharmaceuticals Focus"
subtitle: "Hospital Consumption Data Analysis (Excluding Pharmaceuticals) - 13 Month Study"
author: "Medical Distribution Business Analysis"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cosmo
    highlight: tango
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    number_sections: true
    code_folding: hide
    df_print: paged
    fig_width: 12
    fig_height: 8
---

```{css, echo=FALSE}
/* Enhanced CSS for Non-Pharma Analysis */
body {
  font-family: 'Segoe UI', Tahoma, Geneva, Verdana, sans-serif;
  line-height: 1.6;
  background-color: #f8f9fa;
}

.main-container {
  max-width: 1200px;
  background-color: white;
  box-shadow: 0 0 20px rgba(0,0,0,0.1);
  border-radius: 10px;
  margin: 20px auto;
  padding: 30px;
}

h1, h2, h3 {
  color: #2c3e50;
  border-bottom: 2px solid #3498db;
  padding-bottom: 10px;
}

h1 {
  background: linear-gradient(135deg, #667eea 0%, #764ba2 100%);
  color: white;
  padding: 20px;
  border-radius: 10px;
  text-align: center;
  border-bottom: none;
}

.alert {
  padding: 20px;
  margin-bottom: 25px;
  border: 1px solid transparent;
  border-radius: 8px;
  box-shadow: 0 2px 10px rgba(0,0,0,0.1);
}

.alert-success {
  background: linear-gradient(135deg, #d4edda 0%, #c3e6cb 100%);
  border-color: #c3e6cb;
  color: #155724;
}

.alert-info {
  background: linear-gradient(135deg, #d1ecf1 0%, #bee5eb 100%);
  border-color: #bee5eb;
  color: #0c5460;
}

.alert-warning {
  background: linear-gradient(135deg, #fff3cd 0%, #ffeaa7 100%);
  border-color: #ffeaa7;
  color: #856404;
}

.alert-danger {
  background: linear-gradient(135deg, #f8d7da 0%, #f5c6cb 100%);
  border-color: #f5c6cb;
  color: #721c24;
}

.kpi-box {
  background: linear-gradient(135deg, #e74c3c 0%, #c0392b 100%);
  color: white;
  padding: 25px;
  border-radius: 15px;
  text-align: center;
  margin: 15px;
  box-shadow: 0 5px 15px rgba(0,0,0,0.2);
  transition: transform 0.3s ease;
}

.kpi-box:hover {
  transform: translateY(-5px);
}

.kpi-number {
  font-size: 2.5em;
  font-weight: bold;
  display: block;
}

.kpi-label {
  font-size: 1em;
  opacity: 0.9;
  margin-top: 10px;
}

.exclusion-notice {
  background: linear-gradient(135deg, #ff6b6b 0%, #ee5a52 100%);
  color: white;
  padding: 20px;
  border-radius: 10px;
  text-align: center;
  margin: 20px 0;
  font-weight: bold;
  font-size: 1.1em;
}

.highlight-box {
  background: linear-gradient(135deg, #74b9ff 0%, #0984e3 100%);
  color: white;
  padding: 20px;
  border-radius: 10px;
  margin: 20px 0;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = 'center',
  cache = TRUE
)

# Function to install and load packages
install_and_load <- function(packages) {
  for (package in packages) {
    if (!require(package, character.only = TRUE)) {
      install.packages(package, dependencies = TRUE)
      library(package, character.only = TRUE)
    }
  }
}

# Required packages
required_packages <- c(
  "readr", "dplyr", "ggplot2", "plotly", "DT", 
  "lubridate", "tidyr", "scales", "knitr", 
  "kableExtra", "gridExtra", "viridis", "zoo"
)

# Install and load packages
install_and_load(required_packages)

# Try to load optional packages
if (!require(treemapify, quietly = TRUE)) {
  message("treemapify package not available - treemap visualization will be skipped")
  treemap_available <- FALSE
} else {
  treemap_available <- TRUE
}
```

```{r load-data, include=FALSE}
# Load and prepare data
data <- read_csv("cleanedup_data_and_merged_and_refined.csv")

# Data cleaning
colnames(data) <- gsub(" ", "_", colnames(data))
data <- data %>%
  mutate(
    Date = paste(YEAR, MONTH, "01", sep = "-"),
    Date = as.Date(Date, format = "%Y-%B-%d"),
    Month_Year = format(Date, "%Y-%m"),
    ITEM_NAME = trimws(ITEM_NAME),
    VENDOR = trimws(VENDOR),
    CATEGORY = trimws(CATEGORY)
  )

# EXCLUDE PHARMACEUTICALS FROM ALL ANALYSIS
# Filter out Pharmaceuticals category completely
filtered_data <- data %>%
  filter(CATEGORY != "Pharmaceuticals")

# Get available categories (excluding Pharmaceuticals)
available_categories <- sort(unique(filtered_data$CATEGORY))
excluded_pharma_records <- nrow(data) - nrow(filtered_data)
excluded_pharma_quantity <- sum(data$QUANTITY[data$CATEGORY == "Pharmaceuticals"], na.rm = TRUE)

# Calculate key metrics (on non-pharmaceutical data only)
total_records <- nrow(filtered_data)
total_quantity <- sum(filtered_data$QUANTITY, na.rm = TRUE)
unique_items <- n_distinct(filtered_data$ITEM_NAME)
unique_vendors <- n_distinct(filtered_data$VENDOR)
unique_categories <- n_distinct(filtered_data$CATEGORY)
date_range <- paste(min(filtered_data$Date, na.rm = TRUE), "to", max(filtered_data$Date, na.rm = TRUE))

# Original totals for comparison
original_total_records <- nrow(data)
original_total_quantity <- sum(data$QUANTITY, na.rm = TRUE)
pharma_percentage <- round((excluded_pharma_quantity / original_total_quantity) * 100, 1)
```

<div class="exclusion-notice">
🚫 <strong>PHARMACEUTICALS EXCLUDED</strong> 🚫<br>
This analysis focuses on NON-PHARMACEUTICAL opportunities only<br>
Excluded: `r format(excluded_pharma_records, big.mark = ",")` pharmaceutical records (`r format(excluded_pharma_quantity, big.mark = ",")` units - `r pharma_percentage`% of total volume)
</div>

# Executive Summary {.tabset}

<div class="alert alert-success">
<strong>Strategic Focus:</strong> With pharmaceuticals excluded, this analysis reveals `r format(total_quantity, big.mark = ",")` units of annual consumption across `r unique_categories` non-pharmaceutical medical categories, representing significant untapped distribution opportunities beyond the traditional pharma market.
</div>

<div class="alert alert-info">
<strong>Analysis Scope:</strong> Non-Pharmaceutical Categories Only<br>
<strong>Categories Analyzed:</strong> `r paste(available_categories, collapse = ", ")`<br>
<strong>Market Focus:</strong> Medical supplies, surgical equipment, consumables, and specialized healthcare products
</div>

## Key Performance Indicators

<div style="display: flex; flex-wrap: wrap;">
<div class="kpi-box" style="flex: 1;">
<div class="kpi-number">`r format(total_quantity, big.mark = ",")`</div>
<div class="kpi-label">Non-Pharma Units Consumed</div>
</div>

<div class="kpi-box" style="flex: 1;">
<div class="kpi-number">`r unique_items`</div>
<div class="kpi-label">Unique Non-Pharma Products</div>
</div>

<div class="kpi-box" style="flex: 1;">
<div class="kpi-number">`r unique_vendors`</div>
<div class="kpi-label">Non-Pharma Vendors</div>
</div>

<div class="kpi-box" style="flex: 1;">
<div class="kpi-number">`r unique_categories`</div>
<div class="kpi-label">Medical Categories</div>
</div>
</div>

## Strategic Opportunities (Non-Pharmaceutical Focus)

<div class="highlight-box">
<strong>Why Focus on Non-Pharmaceuticals?</strong>
<ul>
<li><strong>🎯 Less Competition:</strong> Fewer large distributors dominate non-pharma medical supplies</li>
<li><strong>💰 Higher Margins:</strong> Specialized medical equipment and supplies often have better profit margins</li>
<li><strong>🤝 Relationship Building:</strong> Direct relationships with medical departments vs. pharmacy procurement</li>
<li><strong>📈 Growth Potential:</strong> Surgical and specialized equipment markets are rapidly expanding</li>
<li><strong>⚡ Faster Entry:</strong> Fewer regulatory barriers compared to pharmaceutical distribution</li>
</ul>
</div>

<div class="alert alert-info">
<strong>Immediate Non-Pharma Opportunities:</strong>
<ul>
<li><strong>Surgical Supplies:</strong> High-value, complex procurement needs</li>
<li><strong>Medical Consumables:</strong> Steady demand, predictable ordering patterns</li>
<li><strong>Specialized Equipment:</strong> Ortho, cardiology, radiology supplies</li>
<li><strong>Wound Care & Respiratory:</strong> Growing market segments</li>
</ul>
</div>

# Market Analysis (Non-Pharmaceutical)

## ABC Classification Analysis

### What is ABC Analysis for Medical Supplies?

<div class="alert alert-info">
<h4>📊 ABC Analysis for Non-Pharmaceutical Medical Distribution</h4>
<p><strong>ABC Analysis</strong> for medical supplies helps identify which non-pharmaceutical products drive the most volume and revenue opportunity:</p>

<ul>
<li><strong>Class A (High Priority):</strong> High-volume medical consumables, surgical supplies, and equipment that represent <strong>80% of non-pharma consumption</strong>. These include examination gloves, syringes, surgical instruments, and monitoring equipment.</li>

<li><strong>Class B (Medium Priority):</strong> Specialized medical devices and supplies representing <strong>15% of consumption</strong>. These include category-specific instruments, diagnostic supplies, and periodic replacement items.</li>

<li><strong>Class C (Low Priority):</strong> Niche medical supplies and equipment representing <strong>5% of consumption</strong>. These include specialized tools, rarely-used equipment, and emergency-only supplies.</li>
</ul>

<p><strong>Non-Pharmaceutical Distribution Advantages:</strong></p>
<ul>
<li>🎯 <strong>Direct Department Sales:</strong> Sell directly to surgery, radiology, orthopedics departments</li>
<li>💰 <strong>Value-Added Services:</strong> Equipment training, maintenance, custom kitting</li>
<li>📈 <strong>Sticky Relationships:</strong> Equipment compatibility creates vendor loyalty</li>
<li>⚡ <strong>Faster Decision Making:</strong> Department heads vs. pharmacy committees</li>
</ul>
</div>

```{r abc-analysis-nonpharma}
# Perform ABC Analysis on non-pharmaceutical data
abc_analysis <- filtered_data %>%
  group_by(ITEM_NAME, CATEGORY) %>%
  summarise(
    Total_Quantity = sum(QUANTITY, na.rm = TRUE),
    Transaction_Count = n(),
    Avg_Quantity_Per_Transaction = mean(QUANTITY, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  arrange(desc(Total_Quantity)) %>%
  mutate(
    Cumulative_Quantity = cumsum(Total_Quantity),
    Total_All_Items = sum(Total_Quantity),
    Percentage_of_Total = (Total_Quantity / Total_All_Items) * 100,
    Cumulative_Percentage = (Cumulative_Quantity / Total_All_Items) * 100,
    ABC_Class = case_when(
      Cumulative_Percentage <= 80 ~ "A",
      Cumulative_Percentage <= 95 ~ "B",
      TRUE ~ "C"
    )
  )

# ABC Summary
abc_summary <- abc_analysis %>%
  group_by(ABC_Class) %>%
  summarise(
    Items = n(),
    Total_Quantity = sum(Total_Quantity),
    Percentage_of_Volume = (sum(Total_Quantity) / sum(abc_analysis$Total_Quantity)) * 100,
    .groups = 'drop'
  )

kable(abc_summary, 
      caption = "ABC Classification Summary - Non-Pharmaceutical Products Only",
      format.args = list(big.mark = ",")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### High-Priority Non-Pharmaceutical Items (Class A)

```{r class-a-nonpharma-items, echo=FALSE}
class_a_items <- abc_analysis %>%
  filter(ABC_Class == "A") %>%
  select(ITEM_NAME, CATEGORY, Total_Quantity, Transaction_Count, Percentage_of_Total) %>%
  mutate(
    Total_Quantity_Num = Total_Quantity, # Keep numeric for sorting
    Total_Quantity = format(Total_Quantity, big.mark = ","),
    Percentage_of_Total = round(Percentage_of_Total, 2)
  ) %>%
  arrange(desc(Total_Quantity_Num)) # Sort by original numeric quantity

DT::datatable(class_a_items %>% select(-Total_Quantity_Num), 
              caption = "Class A Non-Pharmaceutical Items (High Consumption Volume)",
              rownames = FALSE,
              filter = 'top',
              extensions = 'Buttons',
              options = list(
                pageLength = 25, 
                scrollX = TRUE,
                dom = 'Bfrtip',
                buttons = c('copy', 'csv', 'excel', 'print'),
                columnDefs = list(list(targets = '_all', className = 'dt-center'))
              )) %>%
  formatStyle(columns = 1:ncol(class_a_items %>% select(-Total_Quantity_Num)), fontSize = '12px')
```

<div class="alert alert-success">
<strong>🎯 Strategic Focus: Class A Items</strong>
<p>These items represent approximately 80% of your total non-pharmaceutical consumption volume. Prioritizing these for inventory management, supplier negotiation, and sales efforts will yield the most significant impact.</p>
<ul>
  <li>Ensure high availability and optimal stock levels.</li>
  <li>Negotiate favorable terms with suppliers due to high volume.</li>
  <li>Target hospital departments that heavily utilize these specific items.</li>
</ul>
</div>

### Medium-Priority Non-Pharmaceutical Items (Class B)

```{r class-b-nonpharma-items, echo=FALSE}
class_b_items <- abc_analysis %>%
  filter(ABC_Class == "B") %>%
  select(ITEM_NAME, CATEGORY, Total_Quantity, Transaction_Count, Percentage_of_Total) %>%
  mutate(
    Total_Quantity_Num = Total_Quantity, # Keep numeric for sorting
    Total_Quantity = format(Total_Quantity, big.mark = ","),
    Percentage_of_Total = round(Percentage_of_Total, 2)
  ) %>%
  arrange(desc(Total_Quantity_Num)) # Sort by original numeric quantity

DT::datatable(class_b_items %>% select(-Total_Quantity_Num), 
              caption = "Class B Non-Pharmaceutical Items (Moderate Consumption Volume)",
              rownames = FALSE,
              filter = 'top',
              extensions = 'Buttons',
              options = list(
                pageLength = 25, 
                scrollX = TRUE,
                dom = 'Bfrtip',
                buttons = c('copy', 'csv', 'excel', 'print'),
                columnDefs = list(list(targets = '_all', className = 'dt-center'))
              )) %>%
  formatStyle(columns = 1:ncol(class_b_items %>% select(-Total_Quantity_Num)), fontSize = '12px')
```

<div class="alert alert-info">
<strong>⚙️ Managing Class B Items</strong>
<p>Class B items typically account for the next 15% of consumption volume. While not as critical as Class A, they are still significant.</p>
<ul>
  <li>Maintain standard inventory controls and review stock levels periodically.</li>
  <li>Explore opportunities for consolidating suppliers if multiple vendors provide similar Class B items.</li>
</ul>
</div>

### Low-Priority Non-Pharmaceutical Items (Class C)

```{r class-c-nonpharma-items, echo=FALSE}
class_c_items <- abc_analysis %>%
  filter(ABC_Class == "C") %>%
  select(ITEM_NAME, CATEGORY, Total_Quantity, Transaction_Count, Percentage_of_Total) %>%
  mutate(
    Total_Quantity_Num = Total_Quantity, # Keep numeric for sorting
    Total_Quantity = format(Total_Quantity, big.mark = ","),
    Percentage_of_Total = round(Percentage_of_Total, 2)
  ) %>%
  arrange(desc(Total_Quantity_Num)) # Sort by original numeric quantity

DT::datatable(class_c_items %>% select(-Total_Quantity_Num), 
              caption = "Class C Non-Pharmaceutical Items (Low Consumption Volume)",
              rownames = FALSE,
              filter = 'top',
              extensions = 'Buttons',
              options = list(
                pageLength = 25, 
                scrollX = TRUE,
                dom = 'Bfrtip',
                buttons = c('copy', 'csv', 'excel', 'print'),
                columnDefs = list(list(targets = '_all', className = 'dt-center'))
              )) %>%
  formatStyle(columns = 1:ncol(class_c_items %>% select(-Total_Quantity_Num)), fontSize = '12px')
```

<div class="alert alert-warning">
<strong>📦 Handling Class C Items</strong>
<p>Class C items make up the bulk of your unique product count but only a small fraction (around 5%) of total consumption volume.</p>
<ul>
  <li>Implement simplified inventory controls; consider ordering on demand or in larger, less frequent batches.</li>
  <li>Evaluate if all Class C items are essential or if some can be discontinued or substituted.</li>
</ul>
</div>

<div class="alert alert-secondary" style="margin-top: 20px;">
  <strong>Understanding ABC Classification Tables:</strong>
  <ul>
    <li><strong>Class A:</strong> Vital few items, typically ~80% of volume. High management priority.</li>
    <li><strong>Class B:</strong> Intermediate items, typically next ~15% of volume. Moderate management.</li>
    <li><strong>Class C:</strong> Trivial many items, typically last ~5% of volume. Simpler controls.</li>
  </ul>
  <p>The tables above list all items within each respective class, sorted by their consumption quantity. This allows for detailed review and targeted strategies for each segment of your non-pharmaceutical inventory.</p>
</div>

### Non-Pharmaceutical ABC Visualization

```{r abc-viz-nonpharma, fig.height=10}
# ABC Distribution Chart
abc_plot1 <- ggplot(abc_summary, aes(x = ABC_Class, y = Percentage_of_Volume, fill = ABC_Class)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(round(Percentage_of_Volume, 1), "%")), 
            vjust = -0.5, size = 5, fontface = "bold") +
  scale_fill_manual(values = c("A" = "#e74c3c", "B" = "#f39c12", "C" = "#3498db")) +
  labs(title = "Non-Pharmaceutical ABC Analysis - Volume Distribution",
       subtitle = "Focus on Class A items for maximum non-pharma market impact",
       x = "ABC Class", y = "Percentage of Total Volume") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 12, hjust = 0.5),
    axis.text = element_text(size = 12),
    legend.position = "none"
  )

# Top 15 non-pharma items bar chart
top_15_items <- abc_analysis %>% head(15)

abc_plot2 <- ggplot(top_15_items, aes(x = reorder(ITEM_NAME, Total_Quantity), 
                                      y = Total_Quantity, fill = ABC_Class)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  scale_fill_manual(values = c("A" = "#e74c3c", "B" = "#f39c12")) +
  labs(title = "Top 15 Non-Pharmaceutical Items by Volume",
       x = "Item Name", y = "Total Quantity") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, hjust = 0.5),
    axis.text.y = element_text(size = 10)
  )

grid.arrange(abc_plot1, abc_plot2, nrow = 2)
```

## Non-Pharmaceutical ABC Analysis Summary

```{r abc-summary-nonpharma}
# Calculate detailed ABC insights
abc_insights <- abc_analysis %>%
  group_by(ABC_Class) %>%
  summarise(
    Number_of_Items = n(),
    Total_Volume = sum(Total_Quantity),
    Avg_Volume_per_Item = mean(Total_Quantity),
    Min_Volume = min(Total_Quantity),
    Max_Volume = max(Total_Quantity),
    .groups = 'drop'
  ) %>%
  mutate(
    Percentage_of_Items = (Number_of_Items / sum(Number_of_Items)) * 100,
    Percentage_of_Volume = (Total_Volume / sum(Total_Volume)) * 100
  )

kable(abc_insights %>%
        mutate(
          Total_Volume = format(Total_Volume, big.mark = ","),
          Avg_Volume_per_Item = format(round(Avg_Volume_per_Item, 0), big.mark = ","),
          Min_Volume = format(Min_Volume, big.mark = ","),
          Max_Volume = format(Max_Volume, big.mark = ","),
          Percentage_of_Items = paste0(round(Percentage_of_Items, 1), "%"),
          Percentage_of_Volume = paste0(round(Percentage_of_Volume, 1), "%")
        ),
      caption = "Detailed Non-Pharmaceutical ABC Analysis") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

# Key metrics for summary
class_a_items <- sum(abc_insights$Number_of_Items[abc_insights$ABC_Class == "A"])
class_a_volume_pct <- round(abc_insights$Percentage_of_Volume[abc_insights$ABC_Class == "A"], 1)
class_a_items_pct <- round(abc_insights$Percentage_of_Items[abc_insights$ABC_Class == "A"], 1)

top_single_item <- abc_analysis$ITEM_NAME[1]
top_item_volume <- format(abc_analysis$Total_Quantity[1], big.mark = ",")
top_item_pct <- round(abc_analysis$Percentage_of_Total[1], 2)
```

<div class="alert alert-success">
<h4>🎯 Non-Pharmaceutical Market Opportunities</h4>

<strong>Focused Market Intelligence:</strong>
<ul>
<li>📊 <strong>Class A Focus:</strong> Only `r class_a_items` non-pharma items (`r class_a_items_pct`% of products) drive `r class_a_volume_pct`% of total non-pharmaceutical consumption</li>
<li>🥇 <strong>Top Opportunity:</strong> "`r top_single_item`" represents `r top_item_volume` units (`r top_item_pct`% of non-pharma volume)</li>
<li>💡 <strong>Strategic Advantage:</strong> Non-pharma market is less saturated than pharmaceutical distribution</li>
</ul>

<strong>Non-Pharmaceutical Distribution Strategy:</strong>
<ul>
<li>🎯 <strong>Department-Specific Approach:</strong> Target surgery, radiology, orthopedics, cardiology departments directly</li>
<li>💰 <strong>Value-Added Services:</strong> Offer equipment training, maintenance contracts, custom supply kits</li>
<li>📈 <strong>Relationship Leverage:</strong> Equipment compatibility creates switching costs and vendor loyalty</li>
<li>⚡ <strong>Faster Sales Cycles:</strong> Department managers make quicker decisions than pharmacy committees</li>
</ul>

<strong>Operational Focus Areas:</strong>
<ul>
<li><strong>Class A (High-Volume Consumables):</strong> Examination gloves, syringes, monitoring supplies - daily delivery, safety stock</li>
<li><strong>Class B (Specialized Equipment):</strong> Surgical instruments, diagnostic devices - weekly reviews, just-in-time delivery</li>
<li><strong>Class C (Niche Supplies):</strong> Emergency equipment, rare instruments - quarterly reviews, direct-from-manufacturer</li>
</ul>
</div>

# Category Performance Analysis (Non-Pharmaceutical)

```{r category-performance-nonpharma}
# Category performance metrics (non-pharmaceutical only)
category_performance <- filtered_data %>%
  group_by(CATEGORY) %>%
  summarise(
    Total_Transactions = n(),
    Total_Quantity = sum(QUANTITY, na.rm = TRUE),
    Unique_Items = n_distinct(ITEM_NAME),
    Unique_Vendors = n_distinct(VENDOR),
    Avg_Transaction_Size = mean(QUANTITY, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  arrange(desc(Total_Quantity)) %>%
  mutate(
    Percentage_of_Total = (Total_Quantity / sum(Total_Quantity)) * 100,
    Market_Priority = case_when(
      Percentage_of_Total >= 20 ~ "High Priority",
      Percentage_of_Total >= 5 ~ "Medium Priority",
      TRUE ~ "Low Priority"
    ),
    Business_Opportunity = case_when(
      Percentage_of_Total >= 15 ~ "Major Market",
      Percentage_of_Total >= 5 ~ "Significant Market", 
      TRUE ~ "Niche Market"
    )
  )

# Create and display the table using DT
category_table <- category_performance %>%
  mutate(
    Total_Quantity = format(Total_Quantity, big.mark = ","),
    Avg_Transaction_Size = round(Avg_Transaction_Size, 1),
    Percentage_of_Total = paste0(round(Percentage_of_Total, 1), "%")
  )

# Print the caption
cat("<h4>Non-Pharmaceutical Category Performance Analysis</h4>")

# Use DT::datatable for better HTML rendering
DT::datatable(category_table, 
              options = list(pageLength = 10, dom = 'ft'),
              rownames = FALSE,
              class = 'cell-border stripe')
```

<div class="alert alert-info">
<strong>🏥 Non-Pharmaceutical Category Insights:</strong><br>
<strong>High-Volume Categories:</strong> Focus on categories with >10% market share for immediate impact<br>
<strong>Specialized Markets:</strong> Smaller categories often have higher margins and less competition<br>
<strong>Vendor Fragmentation:</strong> Categories with many vendors offer consolidation opportunities
</div>

## Non-Pharmaceutical Category Visualization

```{r category-viz-nonpharma, fig.height=12}
# Category pie chart (non-pharma only)
pie_plot <- ggplot(category_performance, aes(x = "", y = Percentage_of_Total, fill = CATEGORY)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  labs(title = "Non-Pharmaceutical Market Share by Category") +
  theme_void() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    legend.position = "right"
  ) +
  scale_fill_viridis_d()

# Category bar chart
bar_plot <- ggplot(category_performance, aes(x = reorder(CATEGORY, Total_Quantity), 
                                            y = Total_Quantity, fill = Percentage_of_Total)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  scale_fill_viridis_c() +
  labs(title = "Non-Pharmaceutical Category Volume Distribution", 
       x = "Medical Category", y = "Total Quantity",
       fill = "% of Total") +
  theme_minimal() +
  theme(plot.title = element_text(size = 16, hjust = 0.5)) +
  scale_y_continuous(labels = comma)

grid.arrange(pie_plot, bar_plot, nrow = 2)
```

# Vendor Analysis (Non-Pharmaceutical)

```{r vendor-analysis-nonpharma}
# Vendor performance analysis (non-pharmaceutical only)
vendor_performance <- filtered_data %>%
  group_by(VENDOR) %>%
  summarise(
    Total_Transactions = n(),
    Total_Quantity = sum(QUANTITY, na.rm = TRUE),
    Unique_Items = n_distinct(ITEM_NAME),
    Categories_Served = n_distinct(CATEGORY),
    Avg_Transaction_Size = mean(QUANTITY, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  arrange(desc(Total_Quantity)) %>%
  mutate(
    Market_Share = (Total_Quantity / sum(Total_Quantity)) * 100,
    Vendor_Type = case_when(
      Market_Share >= 10 ~ "Major Non-Pharma Supplier",
      Market_Share >= 5 ~ "Significant Non-Pharma Supplier",
      Market_Share >= 1 ~ "Regular Non-Pharma Supplier",
      TRUE ~ "Small Non-Pharma Supplier"
    )
  )

# Top 15 non-pharma vendors table
top_vendors <- vendor_performance %>% 
  head(15) %>%
  mutate(
    Total_Quantity = format(Total_Quantity, big.mark = ","),
    Avg_Transaction_Size = round(Avg_Transaction_Size, 1),
    Market_Share = round(Market_Share, 2)
  )

kable(top_vendors,
      caption = "Top 15 Non-Pharmaceutical Vendors by Volume") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### Interactive Non-Pharmaceutical Vendor Analysis

```{r vendor-interactive-nonpharma}
# Create interactive vendor table
DT::datatable(vendor_performance %>%
                mutate(
                  Market_Share = round(Market_Share, 2),
                  Avg_Transaction_Size = round(Avg_Transaction_Size, 1)
                ), 
              options = list(pageLength = 10, scrollX = TRUE),
              filter = 'top',
              caption = "Interactive Non-Pharmaceutical Vendor Analysis - Identify Partnership & Consolidation Targets") %>%
  formatStyle(columns = 1:8, fontSize = '11px')
```

## Non-Pharmaceutical Vendor Consolidation Opportunities

```{r vendor-consolidation-nonpharma}
# Identify consolidation opportunities in non-pharma space
consolidation_opportunities <- vendor_performance %>%
  filter(Vendor_Type %in% c("Small Non-Pharma Supplier", "Regular Non-Pharma Supplier")) %>%
  summarise(
    Vendors_to_Replace = n(),
    Combined_Volume = sum(as.numeric(gsub(",", "", Total_Quantity))),
    Combined_Transactions = sum(Total_Transactions),
    Average_Market_Share = mean(Market_Share),
    .groups = 'drop'
  )

kable(consolidation_opportunities,
      caption = "Non-Pharmaceutical Vendor Consolidation Opportunity",
      format.args = list(big.mark = ",")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

<div class="alert alert-warning">
<strong>🎯 Non-Pharma Consolidation Strategy:</strong> `r consolidation_opportunities$Vendors_to_Replace` smaller non-pharmaceutical vendors could be consolidated, representing `r format(consolidation_opportunities$Combined_Volume, big.mark = ",")` units of business opportunity. This market is less competitive than pharmaceuticals, offering better partnership terms.
</div>

# Time Series Analysis (Non-Pharmaceutical)

```{r time-series-nonpharma}
# Monthly trends (non-pharmaceutical only)
monthly_trends <- filtered_data %>%
  group_by(Month_Year) %>%
  summarise(
    Total_Quantity = sum(QUANTITY, na.rm = TRUE),
    Transaction_Count = n(),
    Unique_Items = n_distinct(ITEM_NAME),
    .groups = 'drop'
  ) %>%
  arrange(Month_Year) %>%
  mutate(
    Growth_Rate = (Total_Quantity - lag(Total_Quantity)) / lag(Total_Quantity) * 100,
    Moving_Avg_3M = zoo::rollmean(Total_Quantity, k = 3, fill = NA, align = "right")
  )

kable(monthly_trends %>%
        mutate(
          Total_Quantity = format(Total_Quantity, big.mark = ","),
          Growth_Rate = round(Growth_Rate, 1),
          Moving_Avg_3M = round(Moving_Avg_3M, 0)
        ),
      caption = "Monthly Non-Pharmaceutical Consumption Trends") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

## Monthly Non-Pharmaceutical Trend Visualization

```{r monthly-trends-viz-nonpharma, fig.height=10}
# Monthly consumption plot (non-pharma)
monthly_plot <- ggplot(monthly_trends, aes(x = Month_Year)) +
  geom_line(aes(y = Total_Quantity, group = 1), color = "#e74c3c", size = 1.2) +
  geom_point(aes(y = Total_Quantity), color = "#2c3e50", size = 2) +
  geom_line(aes(y = Moving_Avg_3M, group = 1), color = "#f39c12", size = 1, linetype = "dashed") +
  labs(title = "Monthly Non-Pharmaceutical Consumption Trends",
       subtitle = "Red line: Actual consumption, Orange line: 3-month moving average",
       x = "Month-Year", y = "Total Quantity") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 12, hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  scale_y_continuous(labels = comma)

# Growth rate plot (non-pharma)
growth_plot <- ggplot(monthly_trends %>% filter(!is.na(Growth_Rate)), 
                     aes(x = Month_Year, y = Growth_Rate)) +
  geom_bar(stat = "identity", fill = "#e74c3c") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(title = "Non-Pharmaceutical Month-over-Month Growth Rate",
       x = "Month-Year", y = "Growth Rate (%)") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

grid.arrange(monthly_plot, growth_plot, nrow = 2)
```